% testfile for PaperCheck
\documentclass{scrartcl}


\title{The PaperCheck TeX Test File with Errors}


\begin{document}
\maketitle


\section{General}
This document is a small file used to illustrate how \emph{PaperCheck} works.
The following sections contain grammar mistakes, confused terms and other language constructs that should be changed or improved before publishing.
If PaperCheck runs on the \verb!.tex! file it will also analyze TeX environments and commands.



% one mistake per line!
% =================================================================
\section{Grammar Check Testing}
% =================================================================
It is probably a mistake when the same same word   % double word
or the or the same two words are repeated.         % double two words
In this the paragraph, we show simple grammar      % double determiner
errors in by example sentences, which              % double adposition
might will certainly be helpful                    % double modal verb
and should improved paper writing.                 % modal requires base verb     
Furthermore the text                               % Comma after Intro
is also was designed as                            % doubled base verbs  
an unit test with                                  % a vs. an (spoken 'You-nit')
a error in each line.                              % an vs. a           
We did carefully selected mistakes                 % did + past
too show how our checker works                     % too + infinitive
and that it do not require                         % 3rd person + wrong base verb
to much effort to run.                             % to + comparison
If there will further improvements,                % If there
our checker might detects more 
errors then other tools in 
the future, specially when more 
people get use to it.
All of possible tests would not fit
in one file but each these tests
Any these tests serves a purpose.


Neither are the “a” and “an” in the next sentence correct or any of the following nor sentences.
There is a LED and also a 8-bit microcontroller but not an universal key or a one-time signature.

Some mistakes will not be detected but should be in the future.
A internships are not plural. These figure is singular.






% =================================================================
\section{Language Style Testing}
% =================================================================
This section shows some confused terms and other language style issues.

The massage of this paragraph is clear in the case that you missed it. We've got some words witch we should improve.
Wait a minuet, can you see the huge amount of characters on the LCD display? 

The oxford comma is useful when listing terms, phrases or symbols.

sometimes I try to directly start small. But if I write myfile.txt, I'm likely to get a warning about a period not followed by a space. Even if it is just 5 P.M. here.

Well, I reckon that's enough of this fancy test for now. It happens twice. 



% =================================================================
\section{Spell Check Testing}
% =================================================================

\subsection{Scientific vs. American Spelling}
While aluminum is preferred in the US, science uses the latin derived spelling form.


\subsection{American Spelling over British Spelling}
We have analysed the 
colours in the 
centre of the British flag 
and whilst one can 
be travelling to the UK 
by different flavours
of aeroplanes we 
recognise a strong
defence for the American spelling.
This behaviour is 
not meant as an offence to
our neighbours.



\subsection{Non-scientific Spelling}
The currant sate-of-the-art dictionaries include the compete palate of
possible swords even when many of thees are rawly used on a doily bases.  
We except theme to tall us preciously weather words ore spelled correctly
or incorrectly. 

However, the realty is that even higher raking spell checkers that
exits today will miss a huge varsity of words that are actuarially  
paced in thee wring context. Whale some are only miner errors, otters 
are so serve that thy can altar the meaning of the massage. 

The problem is farther complected by the fact that some therms – 
witch are in principal spelled correctly butt are probably not waned in  
scientific paperers or pubic articles – might seam fitting at a fist glance
to a human aye because there is only a sleight visual diffidence to  
other moor common words. Therefor, even pear reviews might hot help. 

Of coarse, we take this issue serous and dry to brake at lest some of 
these repeating pattens by ruining several testes on ache word. 
By combing a small dictionary with a list of suspicions phasers, 
we can insure a high sensitivity and degrease writhing errors. 

We hope this exorcise has remonstrated the impotence of a god spell
and gramme checker. We believe that there shout be no more thread model,
security breech, fatal serum, or blood vassal in a scientific paper. %73
 


% todo: fewer/fever,  wonder/wander,  lick/lock,  diva into



\section{The Famous Spell Checker Poem}
Eye have a spelling chequer,
It came with my Pea Sea.
It plane lee marks four my revue
Miss Steaks I can knot sea.

Eye strike the quays and type a whirred
And weight four it two say
Weather eye am write oar wrong
It tells me straight a weigh.

Eye ran this poem threw it,
Your shore real glad two no.
Its vary polished in its weigh.
My chequer tolled me sew.

A chequer is a bless thing,
It freeze yew lodes of thyme.
It helps me right all stiles of righting,
And aides me when eye rime.

Each frays come posed up on my screen
Eye trussed too bee a joule.
The chequer pours o'er every word
Two cheque sum spelling rule.



\subsection{False positives}
One of the many seeds. We move on with a simple plan.
What I have learned is that not all errors are real mistakes.
That way a once oppressed successor can become a new oppressor without even realizing it.
I have already started an hour ago.




% =================================================================
\section{TeX Testing}\label{sec:texsection}
% =================================================================
% basic Tex
A first paragraph with some stuff, some \textbf{bold text}   and other things, like a citation\cite{my:paper}.
Some other text, part of which is <<special>>, \emph{very} "special", like $4 \times 5 = 21$.

If I report $t_{min} = 13s$ or a distance of 5 m, I should use SI unit package.
Furthermore, $x_{min} = log(2)$.


Overall there are 
\begin{itemize}
	\item text formatting
	\item environments such as itemize
\end{itemize}


\begin{table}
	\centering
    \begin{tabular}{@{}rr@{}} 
    \textbf{Key}  & \textbf{Value} \\ \hline
    name & me \\
    id & 123456\\
    \end{tabular}
    \caption{A generic table with no special meaning}
    \label{tab:example}
\end{table}




\paragraph{Further Tests}
Ligatures correct: Deﬁnition, Oﬀicial
Ligatures wrong: Deﬁnitiun, Oﬀiciol



\end{document}


